\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Point-Based Outline} }

### 2018-11-11 Outline/OutlineJLin.tex

@@

		\item Graph displaying voter turnout as a function of the registered voters AND voting age population.
		\item Graph displaying voter turnout percentage based on place of residence characteristics by country

@@

@@

	\item Regression: Place of Residence on Liberalism scale - how place influences vision on issues

@@

@@

@@

@@

\begin{enumerate}
\item Variables: The following variables were integrated into the analysis\footnote{The Codebook used as a reference to determine which variables to use is located here: \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part2_variables.txt}}:
\begin{enumerate}
	\item D1004 Election
	\item D1006 Polity Identifier
	\item D1008 Election year
	\item D1010\_1 Weights Sample
	\item D1010\_2 Weights Demographic
	\item D1010\_3 Weights Political 
	\item D1015 Election Type
	\item D2031 Urban/Rural place of Residence
	\item D3014 Self Ideology
	\item D5051\_1 Democracy to Autocracy scale at the time of the election
	\item D5052 Age of Current Regime
	\item D5054 Type of Executive
	\item D5056 Number of Months since last presidential election
	\item D5058 Electoral Formula
\end{enumerate} 
\item Generate alternative measure of ideology based on views of social and economic issues
\begin{enumerate}
	\item Recode the following variables on a scale of 0 = conservative and 1 = liberal with all other points scaled in between. Generates a 9-point scale on liberal views titled {\txt{liberalism}}\footnote{The determination for conservatism and liberalism is based on visions on spending where liberals will be more likely to approve government expenditures and support government social services to people in lieu of the more conservative vision of small government and government staying out of people's lives}
	\begin{enumerate}
		\item D3001 Public Expenditure - Should the government spend more on health, education, unemployment benefits, defense, old age pensions, business and industry, police, welfare benefits
		\item D3004 Income Inequality - Should the government do more to curtail the effects of income inequality
	\end{enumerate}
\end{enumerate}
\item Researcher recode of data: Missing data identified in the codebook as (99 = MISSING) or some other value that reflects that the respondent does not know the response to the question is replaced with a "." to represent missing data
\item Analysis: Stata 15.1 was used to analyze the results
\item Independent Variables:
\begin{enumerate}
	\item Place of Residence - Treated as a categorical variable
	\item Regime Age - Treated as a continuous variable
	\item Level of Democracy - Treated as a categorical variable
	\item Electoral Formula - Treated as a categorical variable
\end{enumerate}
\item Dependent Variable:
\begin{enumerate}
	\item Self Ideology - An individual's self placement on the ideological scale with 00 being most left and 10 being most right
	\item Liberalism - One's stance on the social issues
\end{enumerate}
\item Models 
\begin{enumerate}
	\item Model 1 -- Place of Residence on self-identified ideology
	\item Model 2 -- Place of Residence on objective liberalism scale
\end{enumerate}
\end{enumerate}

>>>>

	\item Popular press gives us a conceptualization of rural and urban dwellers in their places of residences \citep{holloway_burning_2007}. They live relatively different lives that may not be understood by each other. Can this lead to differences between their political behavior and attitudes?

@@

		\item Graph showing the distribution of residence - There are more people interviewed for this survey who live in urban centers than rural villages.

@@

	\item As \cite{holloway_burning_2007} warns, rural residents cannot be treated as a full voting bloc especially if the analyses do not consider the specific differences between the demographics of the residents withing each place of residence itself. For this paper, I will heed to the warning and not overgeneralize in the results. The goal for the analyses is to see if being in a different place compared to your neighbors would influence your voting habits. I do not aim to make predictions of votes based on the results here.
\item Hypotheses
	\item H1: Place of residence matters in one's self-identified political ideology
	\item H2: Place of residence influences how one conceptualizes the issues and states their stances on them
	\item H3: Regime factors such as age, level of democracy, and electoral formula matter to influence how place of residence influences one's stance on the issues

@@

	\item Regression: Place of Residence on Liberalism scale - how place influences vision on issues - the results suggest similar findings to self ideology but the difference is relatively small. When people live in more urban areas, they are more likely to think liberally but that difference does not vary considerably. 
		\item A major caveat for this is that the regime types here are all relatively established democracies and are relatively free based on the "Level of Democracy" measure. Therefore, it may be hard to say that electoral formula, regime age, or level of democracy does not matter. These variables are statistically significant in the regression. Their influence is just not as salient in this particular situation
		\item We see these same patterns for the objectively defined liberalism scale. Yet, in liberalism, the divide is only between urban centers and every-place else. Suburban and small towns do not differ significantly from rural places in terms of their interests. \cite{walks_city-suburban_2005} discusses general differences in interests between urban and rural dwellers that cause their divide in politicians that they favor.

@@

	\item Self-identified position on ideology scale and objective ratings based on stance of issues are influenced by place of residence, but the variation is rather large depending on the country where the individual came from. 
	\item The Literature (most notably \cite{walks_city-suburban_2005} for Canada) notes that the differences between place and voting patters or political ideology is rooted in differences of interests. However, if we look at the breakdown for the interests that compose the liberalism variable, we see that there is nothing in the data that can confirm this suggestion. 
	\item Reflection on the hypotheses
		\item H1: Yes
		\item H2: Yes
		\item H3: Yes, but limited to suburban and small town residents when it comes to self-placement on ideology. For the objective liberalism scale, there is a difference between urban and rural, but not between suburban/small town and rural

@@

		\item If the data reflects minimal differences in interests as the root of the differences in political behavior, what else constitutes the difference in voting patterns?

@@

		\item In some elections/polities, the presence of suburban and/or small town residents are also not recorded, therefore the effect between these regions and the observed results may be influenced by the limitations in data availability. 
		\item The analyses in this study also run on the assumption (similar to the coders'), that the rural to urban categorization is universal across political boundaries.

@@

\begin{enumerate}
\item Variables: The following variables were integrated into the analysis\footnote{The Codebook used as a reference to determine which variables to use is located here: \url{http://www.cses.org/datacenter/module4/data/cses4_codebook_part2_variables.txt}}:
\begin{enumerate}
	\item D1004 Election
	\item D1006 Polity Identifier
	\item D1008 Election year
	\item D1010\_1 Weights Sample
	\item D1010\_2 Weights Demographic
	\item D1010\_3 Weights Political 
	\item D1015 Election Type
	\item D2031 Urban/Rural place of Residence
	\item D3014 Self Ideology
	\item D3005\_LH Voters who cast a ballot in the lower house elections
	\item D5051\_1 Democracy to Autocracy scale at the time of the election
	\item D5052 Age of Current Regime
	\item D5054 Type of Executive
	\item D5056 Number of Months since last presidential election
	\item D5058 Electoral Formula
\end{enumerate} 
\item Generate alternative measure of ideology based on views of social and economic issues
\begin{enumerate}
	\item Recode the following variables on a scale of 0 = conservative and 1 = liberal with all other points scaled in between. Generates a 9-point scale on liberal views titled {\txt{liberalism}}\footnote{The determination for conservatism and liberalism is based on visions on spending where liberals will be more likely to approve government expenditures and support government social services to people in lieu of the more conservative vision of small government and government staying out of people's lives}
	\begin{enumerate}
		\item D3001 Public Expenditure - Should the government spend more on health, education, unemployment benefits, defense, old age pensions, business and industry, police, welfare benefits
		\item D3004 Income Inequality - Should the government do more to curtail the effects of income inequality
	\end{enumerate}
\end{enumerate}
\item Researcher recode of data: Missing data identified in the codebook as (99 = MISSING) or some other value that reflects that the respondent does not know the response to the question is replaced with a "." to represent missing data
\item Analysis: Stata 15.1 was used to analyze the results
\item Independent Variables:
\begin{enumerate}
	\item Place of Residence - Treated as a categorical variable
	\item Regime Age - Treated as a continuous variable
	\item Level of Democracy - Treated as a categorical variable
	\item Electoral Formula - Treated as a categorical variable
\end{enumerate}
\item Dependent Variable:
\begin{enumerate}
	\item Self Ideology - An individual's self placement on the ideological scale with 00 being most left and 10 being most right
	\item Liberalism - One's stance on the social issues
\end{enumerate}
\item Models 
\begin{enumerate}
	\item Model 1 -- Place of Residence on self-identified ideology
	\item Model 2 -- Place of Residence on objective liberalism scale
\end{enumerate}
\end{enumerate}

\clearpage
\nocite{*}
\bibliography{RuralPolitics}
\bibliographystyle{chicago}
